### 2016-09-28 results.tex
cleaning up in Section 4, prior to adding new material

\begin{theorem}\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

\todo{distributional-SS or OW privacy proof for classic BF in the ROM}

>>>>

\begin{theorem}\label{thm3}\label{thm:bf-ow} \todo{Finish typesetting.  Result is on chalkboard.}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\Pi_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}
